Missing Data: Current Practice in Football Research and Recommendations for

### 2020-11-09 paper/paper.Rmd
edit conclusion.

Our survey of articles on football related topics showed that current practice of reporting missing data is poor, with only one in nine studies reporting missingness. We speculate that this result is representative of practice in the wider sports science literature. The extremely low reporting of missing data could suggest that this aspect of analysis receives little attention. To address this issue and assist researchers, we have provided recommendations for reporting and exploring missing data. Researchers should consider these recommendations, and pay greater attention to missing data and its influence on research results.

>>>>

Our survey of articles in football research showed that only one in nine studies reported missingness. We speculate that this result is representative of practice in the wider sports science literature. The low reporting of missing data could suggest that this aspect of analysis receives little attention. To address this issue and assist researchers, we have provided recommendations for reporting and exploring missing data. Researchers should consider these recommendations, and pay greater attention to missing data and its influence on research results.
